Icicle: write once, run once

### 2016-06-02 2016fhpc/section/04-Benchmarks.tex
remove some stuff from benchmarks

We are currently using Icicle in production, over medium-sized datasets (around three hundred gigabytes uncompressed) that fit on a single disk.
While future versions will require incremental computation, the runtime processing medium-sized datasets has been small enough to run over the entire dataset each time.
These initial results have been very promising, and we are currently implementing distribution across multiple machines to handle datasets that are tens of terabytes compressed, and do not fit on a single disk.
Incremental computation becomes more important for this distributed case, as it can potentially avoid copying terabytes of data over the network.

@@

It is also important to note that, as a very constrained streaming language, memory usage of Icicle queries is more or less constant in the input size, and runtime is linear.
This is very important, as new data is received regularly and the input size grows.
This does not appear to be the case with the R script, which continually requires larger computers with more memory, in order to finish in a reasonable time.
One of the benefits of Icicle is allowing data scientists to focus on queries, without having to worry about performance.

>>>>

At Ambiata, we are currently using Icicle in production over medium-sized datasets (around three hundred gigabytes uncompressed) that fit on a single disk.
These initial results have been very promising, and we are currently implementing distribution across multiple machines to handle datasets that are tens of terabytes compressed, and do not fit on a single disk.
Incremental computation is even more important for the distributed case, as it can potentially avoid copying terabytes of data over the network.

@@
